---
title: "DEL data"
output: 
  html_document:
    number_sections: true
    theme: flatly
    toc: true
    toc_float: true
vignette: >
  %\VignetteIndexEntry{my_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# USAGE

Public support is crucial for shaping effective development and foreign aid policies. The Development Engagement Lab (DEL) has conducted comprehensive surveys in France, Germany, Great Britain, and the U.S. to track and analyse public attitudes on foreign aid and engagement with sustainable development. In this R package we provide access to the DEL's data. This data comprises nationally representative panel data (2019 - 2023), repeated cross-sections (2019 - 2024), and several foreign aid subject-specific datasets. DEL has made available 87 datasets totalling 246,352 observations from 129,128 unique respondents. The DEL data will enable scholars and policymakers to produce valuable insights that will generate a better understanding of how citizens think about, and engage with, global poverty and sustainable development.

# ARGUMENTS

This R data package allows to download DEL's data 
```{r setup}
library(DELdata)
```

The data will be loaded to your environment following this name format:data_COUNTRY_TYPE_YEAR_WAVE.  

# AUTHOR

Development Engagement Lab 

# REFERENCES

R Package: dataverse. (2024). dataverse: An R package for working with the Dataverse repository. R package version 0.16.0. Retrieved from https://cran.r-project.org/web/packages/dataverse/index.html

Wickham H, Miller E, Smith D (2023). haven: Import and Export 'SPSS', 'Stata' and 'SAS' Files. R package version 2.5.4, https://github.com/tidyverse/haven, https://github.com/WizardMac/ReadStat, https://haven.tidyverse.org.

Gagolewski M (2022). “stringi: Fast and portable character string processing in R.” Journal of Statistical Software, 103(2), 1–59. doi:10.18637/jss.v103.i02.

