---
title: "DEL data"
output: 
  html_document:
    number_sections: true
    theme: flatly
    toc: true
    toc_float: true
vignette: >
  %\VignetteIndexEntry{my_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# USAGE

# ARGUMENTS

This R data package allows to download DEL's data 
```{r setup}
library(DELdata)
```

The data will be loaded to your environment following this name format: 


# AUTHOR

Development Engagement Lab 

# REFERENCES

R Package: dataverse. (2024). dataverse: An R package for working with the Dataverse repository. R package version 0.16.0. Retrieved from https://cran.r-project.org/web/packages/dataverse/index.html

Wickham H, Miller E, Smith D (2023). haven: Import and Export 'SPSS', 'Stata' and 'SAS' Files. R package version 2.5.4, https://github.com/tidyverse/haven, https://github.com/WizardMac/ReadStat, https://haven.tidyverse.org.

Gagolewski M (2022). “stringi: Fast and portable character string processing in R.” Journal of Statistical Software, 103(2), 1–59. doi:10.18637/jss.v103.i02.

